Experiment 3

### 2021-07-03 experiments/experiment 1/experiment 1.Rmd
update experiments

tmplib <- tempfile()
dir.create(tmplib)

@@

remotes::install_github(
  "opetchey/microxanox",
  ref = microxanox_release,
  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
  build_vignettes = FALSE,
  force = TRUE,
  upgrade = FALSE,
  lib = tmplib
)

library(microxanox, lib.loc = tmplib)

library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

@@

ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
xlims = c(-7, -1)
```

```{r finalise}

>>>>

#tmplib <- tempfile()
#dir.create(tmplib)

@@

# remotes::install_github(
#   "opetchey/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE,
#   lib = tmplib
# )

#library(microxanox, lib.loc = tmplib)

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

@@

### 2021-07-03 experiments/experiment 2/experiment 2.Rmd
update experiments

remotes::install_github(
  "opetchey/microxanox",
  ref = microxanox_release,
  # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
  build_vignettes = FALSE,
  force = TRUE,
  upgrade = FALSE,
  lib = tmplib
)

library(microxanox, lib.loc = tmplib)

library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
```

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474 * 0.5
SB_h_div <- -0.323 * 0.5
PB_gmax_div <- 0.015789474 * 0.5
PB_h_div <- -0.323 * 0.5

@@

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))

@@

ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
xlims = c(-7, -1)
```

>>>>

# remotes::install_github(
#   "opetchey/microxanox",
#   ref = microxanox_release,
#   # auth_token = "ENTER YOUR TOKEN or PROVED AS ENVIRONMENT VARIABLE",
#   build_vignettes = FALSE,
#   force = TRUE,
#   upgrade = FALSE,
#   lib = tmplib
# )

#library(microxanox, lib.loc = tmplib)

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
```

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474 * 0
SB_h_div <- -0.323 * 0
PB_gmax_div <- 0.015789474 * 0
PB_h_div <- -0.323 * 0

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))

@@

#ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
#ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
#xlims = c(-7, -1)
```

### 2021-07-03 experiments/experiment 3/experiment 3.Rmd
update experiments

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474 * 0
SB_h_div <- -0.323  * 0
PB_gmax_div <- 0.015789474  * 0
PB_h_div <- -0.323  * 0

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))

@@

ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
xlims = c(-7, -1)
```

```{r finalise}

>>>>

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474 * 0
CB_h_div <- -0.08 * 0
SB_gmax_div <- 0.015789474
SB_h_div <- -0.323
PB_gmax_div <- 0.015789474
PB_h_div <- -0.323

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 3/data/ss_data.RDS"))

@@

#ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
#ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
#xlims = c(-7, -1)
```
